|

### 2019-09-17 paper.Rmd
fixed error in illustration
placement of fig 1 and fig 2

<!-- Background -->
Data is commonly high-dimensional, and visualisation often relies on some form of dimension reduction. This can be done by taking linear projections, or nonlinear if one considers techniques like multidimensional scaling (MDS) (XXXREF) or t-Distributed Stochastic Neighbor Embedding (t-SNE) (XXXREF). For the purposes here, the focus is on linear projections, in particular as provided by the grand tour [@As85; @BCAH05]. Interactive and dynamic displays can provide information beyond what can be achieved in a static display. The grand tour shows a smooth sequence of interpolated low dimensional projections, and allows the viewer to extrapolate from the low-dimensional shapes to the multidimensional distribution. It is particularly useful for detecting clusters, outliers and non-linear dependence.

@@

Figure \ref{fig:renderFunction} shows slices through 4D solid and hollow geometric shapes. For each shape, the points are generated either uniformly within the shape, or on the surface. This illustrates the ease of distinguishing the solid from the hollow, once slices are made.

@@

\begin{figure*}[ht]
\includegraphics[width=0.4\textwidth]{diagrams/centered-slice.pdf}}
\hspace{5mm}
\centerline{\includegraphics[width=0.4\textwidth]{diagrams/orthogonal-distance.pdf}
\caption{Illustrations of  slicing, through a 3D sphere (left), and deomnstrating the calculation of the orthogonal distance  (right). 3D slicing, can be done by sliding the projection plane along the orthogonal direction: centered at the origin (green) and one off-center at $\mathbf{c}$ (blue). This intuition does not transfer to higher dimensions, and it is best to use orthogonal distance between point and projection plane for computing the slice. Because a projection plane has no specific location, for slicing we can prescribe this, as through the data center, or any other point, $\mathbf{c}$.}
\label{fig:diagrams}
\end{figure*}

### Anchoring

*XXX Do we need a diagram?*

>>>>

<!-- Background -->
Data is commonly high-dimensional, and visualisation often relies on some form of dimension reduction. This can be done by taking linear projections, or nonlinear if one considers techniques like multidimensional scaling (MDS) [@mds] or t-Distributed Stochastic Neighbor Embedding (t-SNE) [@tsne]. For the purposes here, the focus is on linear projections, in particular as provided by the grand tour [@As85; @BCAH05]. Interactive and dynamic displays can provide information beyond what can be achieved in a static display. The grand tour shows a smooth sequence of interpolated low dimensional projections, and allows the viewer to extrapolate from the low-dimensional shapes to the multidimensional distribution. It is particularly useful for detecting clusters, outliers and non-linear dependence.

@@

Figure \ref{fig:renderFunction} shows slices through 4D solid and hollow geometric shapes. For each shape, the points are generated either uniformly within the shape, or on the surface. This illustrates the ease of distinguishing the solid from the hollow, once slices are made. Figure \ref{fig:diagrams} illustrates the slicing method for 3D and higher dimensions.

### Non-central slice

@@

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.4\textwidth]{diagrams/centered-slice.pdf}
\hspace{5mm}
\includegraphics[width=0.4\textwidth]{diagrams/orthogonal-distance.pdf}}
\caption{Illustrations of slicing, through a 3D sphere (left), and deomnstrating the calculation of the orthogonal distance (right). 3D slicing, can be done by sliding the projection plane along the orthogonal direction: centered at the origin (green) and one off-center at $\mathbf{c}$ (blue). This intuition does not transfer to higher dimensions, and it is best to use orthogonal distance between point and projection plane for computing the slice. Because a projection plane has no specific location, for slicing we can prescribe this, as through the data center, or any other point, $\mathbf{c}$.}
\label{fig:diagrams}
\end{figure*}
